### 2019-08-06 defesa/tex/chapter/ellipses.tex
add defesa folder

In this chapter, two versions of the Planar Maximal Covering by Ellipses Problem will be introduced.
Firstly, the axis-parallel variant will be defined and a method for it will be developed. Secondly, the version where there is no axis-parallel constraint and the ellipses can be freely rotated will be introduced.

@@

Firstly, the case with only one ellipse is considered, an instance of the problem is denoted as $MCE(\Pp, a, b)$ where $\Pp$ is a set of points and $(a,b) \in \R_{>0}^2$ is a pair of real numbers called the shape parameters of an ellipse. 
In the general case, every point has weights, but without loss of generality (later explained), this detail will be ignored and the weights are assumed to be unitary.
The notation used here is similar to the one introduced on \autoref{chapter:pmclp}, the ellipse with an undefined center is referred to as $E$. To denote the ellipse with center set to be at point $q$, $E(q)$ is used. Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_pellipse} (in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$). Hence, the problem can be defined as follows.

@@

\begin{definicao}
Let $MCE(\Pp, \E)$ be an instance of the maximal covering by ellipses, an optimal solution is given by

>>>>

In this chapter, the version of the Planar Maximal Covering by Ellipses Problem where every ellipse has to be parallel to the coordinate axis will be introduced and a method for it will be developed.

@@

Firstly, the case with only one ellipse is considered, an instance of the problem is denoted as $MCE(\Pp, a, b)$ where $\Pp$ is a set of points and $(a,b) \in \R_{>0}^2$ is a pair of real numbers called the shape parameters of an ellipse. 
In the general case, every point has weights, but firstly this detail will be ignored and the weights are assumed to be unitary.
The notation used here is similar to the one introduced on \autoref{chapter:pmclp}, the ellipse with an undefined center is referred to as $E$. To denote the ellipse with center set to be at point $q$, $E(q)$ is used. Also, the set of points covered by $E(q)$ is denoted by $E(q) \cap \Pp$, which indirectly defines $E(q)$ to be the set of points that satisfy \autoref{equation:cover_pellipse} (in other words $E(q)$ is the coverage region defined by the ellipse with shape parameters $(a,b)$, located at center $q$). 
Also, to denote the points on the border of $E(q)$ we use the notation $\tilde{E}(q)$, therefore $p \in \tilde{E}(q)$ translates to $p$ being on the border of $E(q)$.
Hence, the problem can be defined as follows.

@@

\begin{definicao}\label{def:MCE}
Let $MCE(\Pp, \E)$ be an instance of the maximal covering by ellipses, an optimal solution is given by

### 2019-08-06 defesa/tex/chapter/pmclp.tex
add defesa folder

In this chapter, the classical version of PMCLP using disks will be defined and a version of the method will be proposed with the intention of later being used to solve the axis-parallel ellipses version of PMCLP. Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$ where $\Pp$ is a set of points and $m$ is the number of unit disks.

@@

Two exact methods for the $MCD(\Pp, 1)$ have been found in the literature. A $\bigO(n^2)$ algorithm is proposed by \cite{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \cite{drezner}.
As it has been mentioned, $MCD(\Pp,1)$ is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real number that sum to $0$, given $n$ real numbers). Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for $MCD(\Pp,1)$, which meant that no better time-complexity could be achieved. Since then, however, better algorithms for 3SUM have been developed with a $\bigO(\frac{n^2}{poly(n)})$ run time complexity \cite{3SUM-kopelowitz:2014}.

@@

Initially, the input of the problem defines a unit disk with its center point undefined, a solution for the problem will then choose a point to be the center of the unit disk, in other words a solution places the disk somewhere in the plane.
We refer to the unit disk with undefined center as $D$. If it is placed at a center $q \in \R^2$, we call it $D(q)$.

\begin{definicao}
    Let $\Pp=\{p_1,\dots,p_n\}$ be a set of $n$ points in $\R^2$, and $w(p)>0, p \in \Pp$ the weight of every point in $\Pp$, we denote $w(A)$, with $A \subset \Pp$, as the sum of weights of every point in $A$. Finally, let $D$ be a unit disk, we define the optimal solution of $MCD(\Pp,1)$ as

@@

Therefore, an optimal solution for an instance of $MCD(\Pp,1)$ will be a point in which a unit disk located at it, covers points whose weights, when summed, is maximal.

@@

In \cite{chazelle:1986, cabello:2006}, on the other hand, the authors instead of working directly with $MCD(P,1)$, introduced an equivalent problem called maximum weight clique. Both methods for this problem consist on building a planar graph on which the vertices were the $\bigO(n^2)$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections. With the graph constructed, a traversal would be done to obtain the answer, thus the time complexity of $\bigO(n^2)$.
The algorithm that we later describe in this work also uses this equivalence. That is why it has been taken to be fundamental to introduce the maximum weight clique problem and discuss the equivalence.

\section{Maximum weight clique}

Let $\Pp=\{p_1,\dots,p_n\}$, with $p\in \R^2$ be a set of points, $\D=\{D_1,\dots,D_n\}$ a set of unit disks, such that $D_i$ is centered at $p_i$, $i=1,\dots,n$, with every disk having a weight $w_i > 0$, $i=1,\dots,n$. A clique, in this context, is a non-empty intersection area of a subset of disks. Note that this is different than the clique problem on a intersection graph (a graph where the vertices are the disks and an edge exists if there is an intersection between two disks). As shown in \autoref{fig:three_disks_no_intersection}, three disks could have non-empty pairwise intersection (which qualifies them as a clique), but the intersection of all the three together is empty. That is why the clique problem for unit disks is also referred to as the maximum geometric clique problem when the condition of common intersection exists and as the maximum graphical clique problem where there is only the pairwise intersection condition \cite{inplace:2014}. The graphical version of the problem was studied by \cite{graphical-clique} where a $\bigO(n^{4.5})$ algorithm was proposed. Also, in \cite{inplace:2014}, a $\bigO(n^2\log{n})$ time in-place algorithm, which needs $\bigO(1)$ extra space, for arbitrary radii disks was proposed.

@@

    \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection}
    \begin{tikzpicture}[scale=0.55]
    %\draw [help lines] (-5,-3) grid (5,3);
    \draw (0,0) circle (1cm) (0.9,1.6) circle (1cm) (-0.9,1.6) circle (1cm);

@@

    \node[below] at (0,0) {\tiny $p_1$};
    \node[below] at (0.9, 1.6) {\tiny $p_2$};
    \node[below] at (-0.9, 1.6) {\tiny $p_3$};

@@

A solution for the maximum weight clique is a set of points $Q$, such that the sum of weights of all disks that cover it is maximized. Even though there could be a use for the whole set $Q$, as this problem is used as a tool to solve another problem, only finding a point from the maximum weight clique is enough. This will become clear when the equivalence is stated. With everything in hands, we can define the maximum weight clique problem as follows

\begin{definicao}\label{def:max_weight_clique}
    Let $\D$ be a set of unit disks and $\Pp$ be a set of points as defined before, an optimal solution for the maximum weight clique problem is given by

@@

As it has been proposed, with the equivalence of the two problems, the optimal solution of the maximum weight clique problem is also the optimal solution of the $MCD(\Pp,1)$, which means that a disk centered at $q$, defined in \autoref{def:max_weight_clique}, will have a maximal weight covering of the set $\Pp$.

Given an instance of $MCD(\Pp,1)$, the equivalent maximum weight clique problem is obtained by defining the set $\D$ to be the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$. A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$, this means that a intersection between some disks is an area where a disk could be placed to cover the corresponding points.

In \autoref{fig:three_disks_no_intersection}, it can be seen that there is no point where a disk could be placed such that it would cover $p_1, p_2$ and $p_3$, nonetheless anywhere, in any of the pairwise intersections, a disk could be placed to cover the two corresponding points.

Formally, in the maximum weight clique problem, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the $MCD(P,1)$ problem. Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the one disk maximal covering problem. It means that $q$ will lie inside the region $\bigcap_{k \in I} D_k$.

\subsection{An algorithm for the maximum weight clique problem}

@@

Without loss of generality, the weights will be ignored, and the method will be described for the maximum clique problem, assuming that every disk has unit weight. Also, it will be assumed that no pair of disks are placed at the same center.

Let $\D$ be a set of $n$ unit disks, a non-empty intersection area of a subset of disks is convex and bounded by the arcs of the disks that are intersecting \cite{inplace:2014}.
This observation makes checking for every disk $\Cc$, every intersection area that is bounded by its arc sufficient in order to find the optimal solution.

\begin{definicao}\label{def:inter_arc}
    Let $D_i$ and $D_j$ be two unit disks that intersect (at least at one point). Also let $(\theta_1, \theta_2) \in [0,2\pi]^2$ be the two angles that the circumferences induced by $D_i$ and $D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$. If $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$. Then, We define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$, also we refer to them as opening and closing intersection angles respectively.
\end{definicao}

@@

    \caption{Three disks and their intersection points}
    \input{tex/img2.tex}
    \fautor
    \label{fig:3disks_intersect}
\end{figure}

In \autoref{fig:3disks_intersect}, it is shown all the intersection points between $D_1$ with $D_2$ and $D_3$, also they are labeled according to \autoref{def:inter_arc}, note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi]$ interval).

With \autoref{def:inter_arc} in hands, we can establish the basis of the algorithm to find the maximum clique that a disk $D_i$ participates: a traversal going through every point of intersection with $D_i$ in counter-clockwise order keeping a set of active disks, when an opening intersection angle is reached, the corresponding disk is added to the active set; when a closing one is reached, the corresponding disk is removed from the active set.
This simple traversal, however, would not handle the special case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ (see \autoref{fig:3disks_intersect}). If the traversal begins at the point with smallest angle, the algorithm would remove $D_3$ from the active disks without first adding it. If there was another disk starting before $\Gamma_-(1,3)$, the algorithm would not have both of them in the active set at the same time, and the optimal solution could end up not being found. This can be worked around repeating the traversal once without resetting the active disks set, that way in the beginning of the second traversal, the active set would contain the disks that have $\Gamma_+(i,j) > \Gamma_-(i,j)$. This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated simulating the traversal repetition (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively). It can be seen that without the repetition, the algorithm would find $2$ as the value of an optimal solution, which is wrong.

@@

\begin{algoritmo}
\caption{Algorithm for $MCD(\Pp, 1)$ with unit weights}\label{algoritmo:mcd_1}
\begin{algorithmic}[1]
\Procedure{$MCD_1$}{$\Pp$}\Comment{Returns the maximum number of disks that have a non-empty.}
\State $Q_{best} \gets \{\}$
\State $ans \gets$ center of $D_1$
\ForAll{$p_i \in \Pp$}
\State Let $D_i$ be the disk with center at $p_i$
\State Let $I_i$ be the set of disks that intersect with $D_i$
\State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$
\State $Q \gets \{D_i\}$ \Comment{The set of active disks}
\For{$cnt=1..2$} \Comment{Do it twice}
\For{$a \in A$}\Comment{Assuming $A$ is sorted}
\State Let $D_a$ be the disk that intersects $D_i$ at angle $a$. 
\If{$a$ is a starting angle}
\State $Q \gets Q \cup \{D_a\}$
\Else
\State $Q \gets Q \setminus \{D_a\}$
\EndIf
\If{$|Q_{best}| < |Q|$}
\State $Q_{best} \gets Q$
\State $ans \gets $ point corresponding to the intersection angle $a$
\EndIf
\EndFor
\EndFor
\EndFor

@@

\begin{lema}\label{lema:disk}
The \autoref{algoritmo:mcd_1} for the maximum clique has a $\bigO((n+K)\log{n})$ run time complexity where $K$ is the number of intersections of the $n$ disks.
\end{lema}

@@

If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.

\section{Multiple disks $MCD(\Pp, m)$}

In \cite{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD(\Pp, m)$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm. Firstly, they solve the sub-problem $MCD(\Pp, 2)$ in $\bigO(n^3\log{n})$. Then for the rest of the points that are not in that solution, it uses the algorithm developed in \cite{chazelle:1986} for the one-disk case checking every possible solution for every one of the disks left.

It can be seen that in any solution of $MCD(\Pp, m)$, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the maximum weight clique problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_1} as a candidate to be the optimal solution. The number of points \autoref{algoritmo:mcd_1} goes through is $\bigO(n^2)$, then checking every possible center for every ellipse yields a $\bigO(n^{2m})$ run-time complexity.
This algorithm is described in \autoref{chapter:ellipses} for the ellipses case.

The choice of developing a different method for the problem, instead of using the one from \cite{cabello:2006}, is taken for the sake of simplicity considering both algorithms achieve similar bounds.

>>>>

In this chapter, the classical version of PMCLP using disks will be defined and a version of the method will be proposed with the intention of later being used to solve the axis-parallel ellipses version of PMCLP. Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$, where $\Pp$ is a set of points and $m$ is the number of unit disks.

@@

Two exact methods for the $MCD(\Pp, 1)$ have been found in the literature. A $\bigO(n^2)$ algorithm is proposed by \cite{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \cite{drezner}.
As it has been mentioned, $MCD(\Pp,1)$ is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real numbers that sum to $0$, given $n$ real numbers). Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for $MCD(\Pp,1)$, which meant that no better time-complexity could be achieved. Since then, however, better algorithms for 3SUM have been developed with a $\bigO(\frac{n^2}{poly(n)})$ run time complexity \cite{3SUM-kopelowitz:2014}.

@@

Initially, the input of the problem defines a unit disk with its center point undefined, a solution for the problem will then choose a point to be the center of the unit disk. In other words, a solution places the disk somewhere in the plane.
We refer to the unit disk with undefined center as $D$. If it is placed at a center $q \in \R^2$, we call it $D(q)$.

\begin{definicao}
    Let $\Pp=\{p_1,\dots,p_n\}$ be a set of $n$ points in $\R^2$ and $w(p)>0, p \in \Pp$, the weight of every point in $\Pp$. We denote $w(A)$, with $A \subset \Pp$, as the sum of weights of every point in $A$. Finally, let $D$ be a unit disk, we define an optimal solution of $MCD(\Pp,1)$ as

@@

Therefore, an optimal solution for an instance of $MCD(\Pp,1)$ will be a point in which a unit disk located at, covers points whose weights, when summed, is maximal.

@@

In \cite{chazelle:1986} and \cite{cabello:2006}, on the other hand, instead of working directly with $MCD(P,1)$, an equivalent problem called Maximum Weight Clique was introduced. The algorithm that we later describe in this work also uses this equivalence. That is why it has been taken to be fundamental to introduce the Maximum Weight Clique Problem and discuss the equivalence.

\section{Maximum Weight Clique Problem}

Let $\Pp=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$, be a set of points, $\D=\{D_1,\dots,D_n\}$ a set of unit disks, such that $D_i$ is centered at $p_i$, $i=1,\dots,n$, with every disk having a weight $w_i > 0$, $i=1,\dots,n$. A clique, in this context, is a non-empty intersection area of a subset of disks. Note that this is different than the clique problem on a intersection graph (a graph where the vertices are the disks and an edge exists if there is an intersection between two disks). As shown in \autoref{fig:three_disks_no_intersection}, three disks could have non-empty pairwise intersection (which qualifies them as a clique), but the intersection of all the three together is empty. That is why the clique problem for unit disks is also referred to as the Maximum Geometric Clique Problem when the condition of common intersection exists and as the Maximum Graphical Clique Problem when there is only the pairwise intersection condition \cite{inplace:2014}. The graphical version of the problem was studied by \cite{graphical-clique}, where a $\bigO(n^{4.5})$ algorithm was proposed. Also, in \cite{inplace:2014}, a $\bigO(n^2\log{n})$ time in-place algorithm\footnote{An in-place algorithm is an algorithm that needs $\bigO(1)$ extra space.} for arbitrary radii disks was proposed. In \cite{chazelle:1986}, the method for the Maximum Geometric Weight Clique Problem consists on building a planar graph on which the vertices were the $\bigO(n^2)$ pairwise intersection of the circumferences and the edges were the arcs of the circumferences connecting the intersections. With the graph constructed, a traversal is done to obtain the answer, thus the time complexity of $\bigO(n^2)$.

@@

    \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection.}
    \begin{tikzpicture}[scale=1]
    %\draw [help lines] (-5,-3) grid (5,3);
    \draw (0,0) circle (1cm) (0.9,1.6) circle (1cm) (-0.9,1.6) circle (1cm);

@@

    \node[below] at (0,0) {$p_1$};
    \node[below] at (0.9, 1.6) {$p_2$};
    \node[below] at (-0.9, 1.6) {$p_3$};

@@

A solution for the Maximum Weight Clique is a set of points $Q$, such that the sum of weights of all disks that cover it is maximized. Even though there could be a use for the whole set $Q$, as this problem is used as a tool to solve another problem, only finding a point from the Maximum Weight Clique is enough. This will become clear when the equivalence is stated. With everything in hands, we can define the Maximum Weight Clique Problem as follows.

\begin{definicao}\label{def:max_weight_clique}
    Let $\D$ be a set of unit disks and $\Pp$ be a set of points as defined before. An optimal solution for the Maximum Weight Clique Problem is given by

@@

As it has been proposed, with the equivalence of the two problems, an optimal solution of the Maximum Weight Clique Problem is also an optimal solution of the $MCD(\Pp,1)$, which means that a disk centered at $q$, defined in \autoref{def:max_weight_clique}, will have a maximal weight covering of the set $\Pp$.

Given an instance of $MCD(\Pp,1)$, the equivalent Maximum Weight Clique Problem is obtained by defining set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$. A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$. This means that a intersection between some disks is an area where a disk could be placed to cover the corresponding points.

In \autoref{fig:three_disks_no_intersection}, it can be seen that there is no point where a disk could be placed such that it would cover $p_1, p_2$ and $p_3$, nonetheless, in any of the pairwise intersections, a disk could be placed to cover the two corresponding points.

Formally, in the Maximum Weight Clique Problem, if a point $q$ lies inside $\bigcap_{k \in I} D_k$, with $I \subset \{1,\dots,n\}$, then a disk centered at $q$ will cover the points $p_k$, with $k\in I$ in the $MCD(P,1)$ problem. Conversely, the same applies for a disk placed at $q$ that covers points $p_k$, with $k \in I$ in the one disk maximal covering problem. It means that $q$ will lie inside region $\bigcap_{k \in I} D_k$.

\subsection{An algorithm for the Maximum Weight Clique Problem}

@@

Without loss of generality, the weights will be ignored, and the method will be described for the Maximum Clique Problem, assuming that every disk has unit weight. Also, it will be assumed that no pair of disks are placed at the same center.

Let $\D$ be a set of $n$ unit disks, a non-empty intersection area of a subset of disks is convex and bounded by the arcs of the disks that are intersecting \cite{inplace:2014}.
With this observation, in order to find an optimal solution, it is sufficient to check, for every disk $D$, every intersection area that is bounded by its arc.

\begin{definicao}\label{def:inter_arc}
    Let $D_i$ and $D_j$ be two unit disks that intersect (at least at one point). Also let $(\theta_1, \theta_2) \in [0,2\pi]^2$ be the two angles that the circumferences induced by $D_i$ and $D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$. If $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$. Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$, also we refer to them as opening and closing intersection angles respectively.
\end{definicao}

@@

    \caption{Three disks and their intersection points.}
    \input{tex/img2.tex}
    \fautor
    \label{fig:3disks_intersect}
\end{figure}

In \autoref{fig:3disks_intersect}, it is shown all the intersection points between $D_1$ with $D_2$ and $D_3$. Also, they are labeled according to \autoref{def:inter_arc}. Note that $\Gamma_+(1,3) > \Gamma_-(1,3)$ (the angles should be in the $[0,2\pi]$ interval).

With \autoref{def:inter_arc} in hand, we can establish the basis of the algorithm to find the maximum clique in which a disk $D_i$ participates: a traversal going through every point of intersection with $D_i$, in counter-clockwise order, keeping a set of active disks. When an opening intersection angle is reached, the corresponding disk is added to the active set; when a closing one is reached, the corresponding disk is removed from the active set.
This simple traversal, however, would not handle the special case with $\Gamma_+(i,j) > \Gamma_-(i,j)$ (see \autoref{fig:3disks_intersect}). If the traversal begins at the point with smallest angle, the algorithm would remove $D_3$ from the active disks without first adding it. If there was another disk starting before $\Gamma_-(1,3)$, the algorithm would not have both of them in the active set at the same time, and an optimal solution could end up not being found. This can be worked around repeating the traversal once without resetting the active disks set, that way, in the beginning of the second traversal, the active set would contain the disks that have $\Gamma_+(i,j) > \Gamma_-(i,j)$. This is shown in \autoref{fig:array_disks}, where the intersections list is duplicated, simulating the traversal repetition (note the indication to where the traversal starts as well as the positive and negative signs representing when a intersection with another disk opens and closes, respectively). It can be seen that without the repetition, the algorithm would find $2$ as the value of an optimal solution, which is wrong.

@@

\begin{algoritmo}
\caption{Algorithm for $MCD(\Pp, 1)$ with unit weights}\label{algoritmo:mcd_1}
\begin{algorithmic}[1]
\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$.}
\Ensure{The maximum number of points that can be covered by a unit disk.}

\item[]

\Procedure{$MCD_1$}{$\Pp$}
\State $Q_{best} \gets \{\}$
\State $ans \gets$ center of $D_1$
\ForAll{$p_i \in \Pp$}
\State Let $D_i$ be the disk with center at $p_i$
\State Let $I_i$ be the set of disks that intersect with $D_i$
\State $A \gets \{\}$ \Comment{The multiset of intersection angles with $D_i$.}

\ForAll{$j \in I_i$}
\State $A \gets A \cup \{\Gamma_+(i,j) \cup \Gamma_-(i,j)\}$
\EndFor

%\State $A = \bigcup_{j \in I_i} \Gamma_+(i,j) \cup \Gamma_-(i,j)$
\State $Q \gets \{D_i\}$ \Comment{The set of active disks.}
\For{$cnt=1..2$} \Comment{Do it twice.}
\For{$a \in A$}\Comment{Assuming $A$ is sorted.}
\State Let $D_a$ be the disk that intersects $D_i$ at angle $a$. 
\If{$a$ is a starting angle}
\State $Q \gets Q \cup \{D_a\}$
\Else
\State $Q \gets Q \setminus \{D_a\}$
\EndIf
\If{$|Q_{best}| < |Q|$}
\State $Q_{best} \gets Q$
\State $ans \gets $ point corresponding to the intersection angle $a$
\EndIf
\EndFor
\EndFor
\EndFor

@@

\begin{lema}\label{lema:disk}
\autoref{algoritmo:mcd_1} for solving the Maximum Clique Problem has a $\bigO((n+K)\log{n})$ run time complexity, where $K$ is the number of intersections of the $n$ disks.
\end{lema}

@@

If a simpler implementation is desired, or the number of intersections is large, determining the set $I_i$ (the set of disks that intersect with $D_i$, defined in \autoref{algoritmo:mcd_1}) can be simply done in $\bigO(n^2)$, making the algorithm have a worst-case complexity of $\bigO(n^2\log{n})$.

\section{Multiple disks, $MCD(\Pp, m)$}

In \cite{cabello:2006}, a $\bigO(n^{2m-1}\log{n})$ algorithm for $MCD(\Pp, m)$ is developed as a sub-routine for its $(1-\epsilon)$-approximation algorithm. Firstly, they solve the sub-problem $MCD(\Pp, 2)$ in $\bigO(n^3\log{n})$. Then for the rest of the points that are not in that solution, it uses the algorithm developed in \cite{chazelle:1986} for the one-disk case, checking every possible solution for every one of the disks left.

Also, in \cite{zhou} an heuristic method for large-scale $MCD$ is proposed. It uses a probabilistic algorithm called mean-shift which is a gradient ascent method proven to converge to a local density maxima of any probability distribution. The mean-shift is utilized to find good candidates of centers for the unit disks, then the method backtracks to find the best assignment. The results showed that the greedy algorithm achieves an optimal coverage in some instances, but for some other ones it has a 15 percent worse coverage ratio.

It can be seen that in any solution of $MCD(\Pp, m)$, a disk placed at a point $q$ that covers at least one point $p \in \Pp$ has a correspondence to the Maximum Weight Clique Problem: the point $q$ is inside an intersection area of at least one disk and that area is bounded by some disk, which means it will be checked by \autoref{algoritmo:mcd_1} as a candidate to be an optimal solution. The number of points \autoref{algoritmo:mcd_1} goes through is $\bigO(n^2)$, then checking every possible center for every ellipse yields a $\bigO(n^{2m})$ run-time complexity.
This algorithm is described in \autoref{chapter:ellipses} for the ellipses case.

The choice of developing a different method for the problem, instead of using the one from \cite{cabello:2006}, is taken for the sake of simplicity, considering both algorithms achieve similar bounds.

### 2019-08-06 drafts/3points-ellipse5.tex
add defesa folder

	Voltando para a equação anterior obtemos:

	\begin{align*}
	x = \frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2}\\
	y = mx\\
	y = m\frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2}
	\end{align*}

	Tomando a área do triangulo obtemos, veja que $s$ é conhecida dado $h$:

	\begin{align*}
	m\frac{Ah+(	A(\alpha h - h) -\alpha hm + Cm^2h\alpha)}{A-m + Cm^2} \times h = s\\
	A(mh^2\alpha) - h^2m^2\alpha + Cm^3h^2\alpha = s(A-m+Cm^2)\\
	A(mh^2\alpha -s) + C(m^3h^2\alpha -sm^2) = h^2m^2\alpha\\
	A\beta_1 + C\beta_2 + \beta_3 = 0
	\end{align*}
\end{document}

>>>>

	\subsubsection{Domínio $A$}

	A função $h^2$ não está definida para todo $A$. Como $A$ pode ser encontrado em função de $t = tan(2\theta)$, em que $\theta$ é o angulo de rotação da elipse, omitindo-se as contas temos:

	\begin{align}
	A = \frac{-w + \sqrt{t^2 + 1}}{2tw}\\
	\lim\limits_{t\to \infty} A = \frac{1}{2w}\\
	\lim\limits_{t\to 0^+} A = \infty\\
	A' = -\frac{w + \frac{1}{\sqrt{t^2+1}}}{2wt^2} < 0
	\end{align}

	Logo, o domínio de $A$ é $\left[\dfrac{1}{2w}, \infty\right)$.

	Vamos propor que $h$ é uma função monótona. Portanto, será possível aplicar o algoritmo da bisseção para encontrar a resposta.

	A partir desse definição de $A$, também obtemos que $C = A + \frac{1}{t}$, ou seja $C > A$.

	\subsection{Monotonicidade}

	É possível, calculando a derivada de $C$ em função de $A$, ver que $C$ é crescente.
	Como $\Delta>0$ e $\Delta'>0$, verificamos a seguir que $H$ é crescente:
	\begin{align*}
	(A+C-\sqrt{1+(A-C)^2})' = 1 + C' - \frac{(A-C)(1-C')}{\sqrt{1+(A-C)^2}}
	\end{align*}
\end{document}
